Unshuffling Permutations

### 2016-02-10 submission.tex
LATIN 2016

Let us now provide some definitions about graphs and oriented perfect 
matchings that are used in the sequel. If $G$ is an oriented graph 
without loops, two different edges of $G$ are {\em independent} if they 
do not share any common vertex. We say that $G$ is an 
{\em oriented matching} if all edges of $G$ are pairwise independent. 
Moreover, $G$ is {\em perfect} if any vertex of $G$ belongs to at least 
one arc. For any permutation $\pi$ of $S_n$, an 
{\em oriented perfect matching on $\pi$} is an oriented perfect matching 
$\mathcal{M}$ on the set of vertices $[n]$. In the sequel, we shall 
consider a natural notion of pattern avoidance in oriented perfect 
matchings on permutations. For instance, an oriented perfect matching 
$\mathcal{M}$ on a permutation $\pi$ {\em admits an occurrence} of the 
pattern $\CrossingRL$ if there are four positions $i < j < k < \ell$ in 
$\pi$ such that $(\pi(k), \pi(i))$ and $(\pi(j), \pi(\ell))$ are arcs of 
$\mathcal{M}$. When $\mathcal{M}$ does not admit any occurrence of a 
pattern $\mathcal{P}$, we say that $\mathcal{M}$ {\em avoids}~$\mathcal{P}$.

>>>>

Let us now provide some definitions about graphs and oriented perfect
matchings that are used in the sequel. If $G$ is an oriented graph
without loops, two different edges of $G$ are {\em independent} if they
do not share any common vertex. We say that $G$ is an
{\em oriented matching} if all edges of $G$ are pairwise independent.
Moreover, $G$ is {\em perfect} if any vertex of $G$ belongs to at least
one arc. For any permutation $\pi$ of $S_n$, an
{\em oriented perfect matching on $\pi$} is an oriented perfect matching
$\vv{\mathcal{M}}$ on the set of vertices $[n]$. In the sequel, we shall
consider a natural notion of pattern avoidance in oriented perfect
matchings on permutations. For instance, an oriented perfect matching
$\vv{\mathcal{M}}$ on a permutation $\pi$ {\em admits an occurrence} of the
pattern $\CrossingRL$ if there are four positions $i < j < k < \ell$ in
$\pi$ such that $(\pi(k), \pi(i))$ and $(\pi(j), \pi(\ell))$ are arcs of
$\vv{\mathcal{M}}$. When $\mathcal{M}$ does not admit any occurrence of a
pattern $\mathcal{P}$,
we say that $\vv{\mathcal{M}}$ {\em avoids}~$\mathcal{P}$.
